---
title: "Rendering yamlrmd files"
subittle: Vignette
output: 
  rmarkdown::html_vignette:
    toc: TRUE
    number_sections: TRUE
vignette: >
  %\VignetteIndexEntry{rendering-yamlrmd}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Setup

```{r setup}
library(teachertools)
library(tidyverse)  # data wrangling
```


# Get example r/exams exercise file

```{r}
exam_file_path <- "https://raw.githubusercontent.com/sebastiansauer/r-exams-demo/main/exs/swisscapital.Rmd"

ex <- read_lines(exam_file_path)
```


You can have a glimpse into that file [here, in its repo on Github](https://github.com/sebastiansauer/r-exams-demo/blob/main/exs/swisscapital.Rmd).

First few lines:

```{r}
head(ex, 10)
```


# First step: Parse the file


```{r}
ex_parsed <- parse_examfile(exam_file_path)
```


Let's have a look:

```{r}
ex_parsed
```


# Second step: Write as Yaml Rmd file



```{r}
out1 <- write_yamlrmdfile(ex_parsed = ex_parsed, path_output = "~/tmp")
```

I have chosen the folder `tmp` on my root level. Feel free to adapt to your hard disk.

Let's have a look at this file:

```{r}
rendered_yamlrmd_path <- "~/tmp/swisscapital/swisscapital.Rmd"
rendered_yamlrmd <- read_lines(rendered_yamlrmd_path)

head(rendered_yamlrmd)
```

Ok, let's have a look at the whole file:

```{r}
print(rendered_yamlrmd)
```


The function returns the string which is written as the output file:
```{r}
head(out1)
out1
```



# Both steps in one go


```{r}
out2 <- exam2yamlrmd(examfile = exam_file_path,
                    path_output = "~/tmp")
```


```{r}
out2
```



# Alternative way

There's one more convenience function, similar to `exam2yamlrmd` but it allows to render multiple outputformats in one go.

Here, the exam file should be available on the local disk.

```{r}
ex_file <- "swisscapital.Rmd"
```



```{r}
#undebug(render_exs)
render_exs(exs = ex_file,
           render_html = TRUE,
           render_yamlrmd = TRUE,
           render_pdf_print = FALSE,
           my_edir = "/Users/sebastiansaueruser/Rlibs/teachertools/extdata",
           output_path = "~/tmp")
```

